Time invariant analysis of epidemics with \pkg{EpiCompare}

### 2021-03-25 jss/EpiCompare-paper/EpiCompare-paper.Rmd
Added a few sentences to 2.1 to address some of the purple text.

Time-invariance analysis, as it appears in \pkg{EpiCompare}, \sout{can be seen as an attempt to escape} \shannon{bypasses}  many difficulties \shannon{in} comparing different epidemics. With time-invariant analysis, comparing the decades-long outbreak of HIV in the US to a 10 day outbreak of norovirus on a cruise ship is \sout{still} possible. Time-dependent problems can arise when estimation of certain epidemiological parameters, including the reproductive number $R_0$, which \citet{Gallagher2020} show can be \sout{heavily impacted} \shannon{strongly effected} by choices of beginning and ending time points of an epidemic.

@@

$R_0$ is probably the most famous time-invariant numerical summary of an epidemic and is \shannon{often} associated with the Susceptible-Infectious-Recovered (SIR) model \citep{hethcote2001}. For a demonstration of $R_0$ getting lost in a time-dependent analysis we introduce the \citet{Kermack1927}’s common SIR model. This model captures the transitions from one state to the next as a system of ordinary differential equations, where $N$ is the total number of individuals, $\beta$ is the rate of infection, and $\gamma$ is the rate of recovery,

>>>>

Time-invariance analysis, as it appears in \pkg{EpiCompare}, \sout{can be seen as an attempt to escape} \shannon{bypasses}  many difficulties \shannon{in} comparing different epidemics. With time-invariant analysis, comparing the decades-long outbreak of HIV in the US to a 10 day outbreak of norovirus on a cruise ship is \sout{still} possible. Time-dependent problems can arise when estimation of certain epidemiological parameters, including the reproduction number $R_0$.

@@

$R_0$ is probably the most famous time-invariant numerical summary of an epidemic and is \shannon{often} associated with the Susceptible-Infectious-Recovered (SIR) model \citep{hethcote2001}.  \shannon{$R_0$ is a one-number summary of a disease and is defined as the expected number of infections caused by a single infector who is added to a naive population \citep{anderson1992}. $R_0$ can be a difficult quantity to estimate and is typically sensitive to time-based parameters such as the beginning and end of an epidemic \citep{Gallagher2020}. } To demonstrate the difficulty of discerning $R_0$in a time-dependent analysis, we \shannon{first} introduce the \citet{Kermack1927}’s common SIR model. This model captures the transitions from one state to the next as a system of ordinary differential equations, where $N$ is the total number of individuals, $\beta$ is the rate of infection, and $\gamma$ is the rate of recovery,

### 2021-03-25 jss/EpiCompare-paper/EpiCompare-paper.tex
Added a few sentences to 2.1 to address some of the purple text.

Time-invariance analysis, as it appears in \pkg{EpiCompare},
\sout{can be seen as an attempt to escape} \textcolor{orange}{bypasses}
many difficulties \textcolor{orange}{in} comparing different epidemics.
With time-invariant analysis, comparing the decades-long outbreak of HIV
in the US to a 10 day outbreak of norovirus on a cruise ship is
\sout{still} possible. Time-dependent problems can arise when estimation
of certain epidemiological parameters, including the reproductive number
\(R_0\), which \citet{Gallagher2020} show can be \sout{heavily impacted}
\textcolor{orange}{strongly effected} by choices of beginning and ending
time points of an epidemic.

@@

\(R_0\) is probably the most famous time-invariant numerical summary of
an epidemic and is \textcolor{orange}{often} associated with the
Susceptible-Infectious-Recovered (SIR) model \citep{hethcote2001}. For a
demonstration of \(R_0\) getting lost in a time-dependent analysis we
introduce the \citet{Kermack1927}'s common SIR model. This model
captures the transitions from one state to the next as a system of
ordinary differential equations, where \(N\) is the total number of
individuals, \(\beta\) is the rate of infection, and \(\gamma\) is the
rate of recovery,

>>>>

Time-invariance analysis, as it appears in \pkg{EpiCompare},
\sout{can be seen as an attempt to escape} \textcolor{orange}{bypasses}
many difficulties \textcolor{orange}{in} comparing different epidemics.
With time-invariant analysis, comparing the decades-long outbreak of HIV
in the US to a 10 day outbreak of norovirus on a cruise ship is
\sout{still} possible. Time-dependent problems can arise when estimation
of certain epidemiological parameters, including the reproduction number
\(R_0\).

@@

\(R_0\) is probably the most famous time-invariant numerical summary of
an epidemic and is \textcolor{orange}{often} associated with the
Susceptible-Infectious-Recovered (SIR) model \citep{hethcote2001}.
\textcolor{orange}{$R_0$ is a one-number summary of a disease and is defined as the expected number of infections caused by a single infector who is added to a naive population \citep{anderson1992}. $R_0$ can be a difficult quantity to estimate and is typically sensitive to time-based parameters such as the beginning and end of an epidemic \citep{Gallagher2020}. }
To demonstrate the difficulty of discerning \(R_0\)in a time-dependent
analysis, we \textcolor{orange}{first} introduce the
\citet{Kermack1927}'s common SIR model. This model captures the
transitions from one state to the next as a system of ordinary
differential equations, where \(N\) is the total number of individuals,
\(\beta\) is the rate of infection, and \(\gamma\) is the rate of
recovery,
